\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here


\usepackage{fullpage}
\usepackage{multicol}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Sander Demeester} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Dubbelsingel 6} % Your address
\moveleft.5\hoffset\centerline{Brugge, Sint-kruis}
\moveleft.5\hoffset\centerline{04 76 86 48 84}
\moveleft.5\hoffset\centerline{demeester.sander@gmail.com}
\moveleft.5\hoffset\centerline{www.sanderdemeester.be}
\moveleft.5\hoffset\centerline{1990/01/17}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{Personal}
I'm Diagnosed with autism, Because of this, my academic career is somewhat unconventional. My big passions are information networks and number theory.
%----------------------------------------------------------------------------------------
%	Werk ervaring
%---------------------------------------------------------------------------------------- 
\section{Work experience}
{\sl Software developer} \hfill Summer intern 2013 \\
Developing of a Python program to analyze large amount of logging information generated by the Ugent supercomputer through static data analysis and machine learning algorithms.
At High performance and computing infrastructure (University Ghent).\\ (github.com/hpcugent)

{\sl administrative and ICT employee} \hfill 2010 - 2011 \\
Stage at Province of West Flanders department ICR. \\
In my final year of secondary education I started doing some administrative. This work quickly evolved to ICT work. At the end of the year the result was a security model i had developed involving the WiFi Security specification (802.11i)

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

{\sl Secondary education,} Extraordinary education for people with autism.\\
\textbf{Spermalie} BRUGES (2002 - 2010)
\\ \\
\textbf{{\sl Informatics,} Ghent University.\\}
Courses passed:\\
\begin{tabular}{l l l}
1st bachelor (2010-2011) & Programming 1 and 2 \\
                         & Communication Skills \\
                         & Intellectual property law \\
                         & Linux Computing (advanced) \\
                         & Scripting Languages (advanced use of Linux) \\
\\
1st, 2nd and 3rd bachelor (2010-2013) & Algorithms and Data Structures \\
\\
2nd bachelor (2011-2012) & Software Development 1 and 2 \\
                         & Computer Architecture \\
\\
3rd bachelor (2011-2012) & Operating Systems \\
                         & Computer Networking \\
                         & Interdisciplinary Project \\
                         & Internet technology \\
\\
1st master (2012-2013) & Information Security and Cryptography \\
                       & Study of programming languages and models \\
\end{tabular}
\\ \\
\section{Language knowledge}
Dutch (Native speaker) \\
English (Fluent reading, writing and speaking)
 
%----------------------------------------------------------------------------------------
% Opleiding gerelateerde projecten.
%----------------------------------------------------------------------------------------

\section{Education related \\ projects.} 

{\sl Algorithms \& Data Structures:} AD3zip, ZW-tree \\
Own implementation of data compression algorithms.
\begin{itemize}
\item Burrows Wheeler
\item lz77
\item Huffman
\end{itemize}
{\sl Avank-bebras:} Interdisciplinary Project \\
System administrator \& Software developer. \\
http://github.com/SanderDemeester/bebras-avank.
\\ \\
{\sl Project information security:} Designing and implementing of an online banking application using a multi-factor authentication scheme on Android (HOTP).
 
%----------------------------------------------------------------------------------------
%	Niet opleiding gerelateerde projecten
%----------------------------------------------------------------------------------------
 
\section{Personal projects}
	
{\sl Design, configuration and management of an advanced home network} \\
I have built and now maintain an IPv6 home network by running OpenBSD on embedded platforms: Alix 2D2 (AMD Geode, x86) and raspberry PI (ARMv6).\\
Building compute cluster with raspberry PI.

{\sl Author of several open source projects.} \\
Refer to github.com/SanderDemeester
\begin{itemize} \itemsep -2pt
\item Network analysis tools
\item Own implementation of cryptographic algorithms (with the purpose of gaining a better understanding of their inner workings).
\end{itemize}

{\sl ZeusWPI} \\
Active member of ZeusWPI, a student organization at Ghent University with a passion for IT projects.
\begin{itemize} \itemsep -2pt
\item{http://zeus.ugent.be}
\item{http://github.com/ZeusWPI}
\end{itemize}

{\sl Ethical Hacking Workgroup} \\
Active member of the Ethical Hacking Workgroup at the ELIS department of Ghent University, a faculty-organized initiative striving to teach interested students about IT security.

{\sl Attend IT-related conferences \& events}
\begin{itemize} \itemsep -2pt
\item FOSDEM - Free and Open Source Developers, European Meeting (2007-2013)
\item BruCON - annual security and hacker conference (2012)
\item VPW - Flemish programming contest (2011-2013)
\item Blackberry developer conference (2012)
\end{itemize}

{\sl SHA3 workshop} \\
Cryptography workshop about SHA3 and permutation based cryptography, organized by VUB. 


{\sl Reading international academic publications from IEEE and ACM.}

%----------------------------------------------------------------------------------------
%	Kennis sectie
%---------------------------------------------------------------------------------------- 
\end{resume}
\newpage
\section{Computer literacy}

\subsection{Programming languages}
\begin{multicols}{2}
\begin{enumerate}
\item[-] Java (Excellent)
\item[-] C / C++ (Good)
\item[-] Python (Good)
\item[-] Javascript (Good)

\item[-] .NET
\subitem ASP.NET
\item[-] x86 assembler en ARM assembly (Good)
\item[-] Scripting
\subitem Bash, Sed en awk.
\subitem Powershell.
\subsubsection*{Frameworks en Library}
\item[-] libxml2
\item[-] ncurses
\item[-] Play framework
\item[-] Android (basic)
\item[-] Sage Mathematics
\item[-] scikit-learn
\item[-] JDBC
\item[-] jbox2d
\item[-] Swing
\item[-] sigma.js
\item[-] node.js
\end{enumerate}
\end{multicols}
\subsection{System administrator}
\begin{itemize}
\item[-] Linux en OpenBSD
\subitem DNS/BIND (dnssec)
\subitem advanced knowledge of TCP/IP and networking techniques.
\subitem Good knowledge of IPv6 + deploy techniques.
\subitem Knowledge VPN technologies. (TLS/IPSEC)
\subitem Routing and dispatching algorithms (RIPv2, BGP basic).
\subitem Excellent knowledge of the two biggest firewall based rule engines (IPTables and PF).
\subitem Experience with NetFlow packet analysis.
\subitem Experience with Apache.
\subitem Experience with OpenSSL.
\subitem Network Engineering.
\subitem Network Architecture.
\item[-] Experience with Windows, Linux (Debian based, Gentoo, CentOS en BackTrack) and OpenBSD.
\subitem Scripting, bash, sed en awk.
\end{itemize}
\begin{multicols}{2}
\subsection*{Tools}
\begin{enumerate}
\item[-] Wireshark
\item[-] Postgresql
\item[-] MySQL
\item[-] NoSQL
\item[-] Graylog2
\item[-] Logstash
\item[-] Jenkins
\item[-] ZAP
\item[-] Eclipse
\end{enumerate}
\end{multicols}
\subsection{Varia}
\begin{enumerate}
\item[-] Blog (http://www.sanderdemeester.be/blog)
\item[-] Interst in semantic web en Linked Data
\item[-] Continuous integration.
\item[-] OWASP
\item[-] Version control
\subitem git
\subitem basic knowledge SVN
\subitem basic knowledge Mercurial SCM.
\item[-] Basic knowledge databank normalization
\end{enumerate}
\section{References}
{\sl Luis Fernando Munoz \hfill HPC Systems engineer at Ghent University \\
luis.munoz@ugent.be
}

{\sl Jens Timmerman \hfill System Engineer HPC at Ghent University \\
jens.timmerman@ugent.be
}

{\sl Kenneth Hoste \hfill HPC system administrator at Ghent University \\
kenneth.hoste@ugent.be
}

{\sl Jeroen De Wachter \hfill IT Consultant at Addestino  \\
jeroen.de.wachter@telenet.be
}
\end{document}